Neural dialogue act recognition with transformer pre-training

### 2019-04-07 abstract.tex
small edits

Dialogue acts depend on their conversational context.
For example, a speaker may use \textit{okay} to agree with their interlocutor, answer a yes-no question in the affirmative, 
or simply acknowledge the previous utterance, depending on what has transpired in the conversation so far.
Naturally, many strategies attempt to model discourse context in addition to considering the content of the utterance in question.
\cite{stolckeDialogueActModeling2000}, for example, use a Hidden Markov Model to tag dialogue acts.
The hidden state of neural sequence models can also be used to represent discourse context 
\citep[e.g.][]{kalchbrennerRecurrentConvolutionalNeural2013,tranPreservingDistributionalInformation2017}.

@@

However, given that BERT is pre-trained on book and encyclopedia data, 
there is no guarantee it will improve performance on dialogue-specific tasks.
Adding to that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
To assess BERT's potential for dialogue applications, we propose a series of DAR experiments 
with various utterance encoders, including BERT.
Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts.
In particular, we are interested in whether BERT can be fine-tuned to adequately represent
dialogue-specific features such as discourse markers, disfluency, and laughter.

@@

\paragraph{Model.}
The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
For the sequence model, we use a simple RNN.
Conceptually the hidden state of this RNN represents the discourse context which, 
together with the encoded utterance, is used to predict the discourse act tag.

@@

\paragraph{Experiments.}
Our aim is to test the effectiveness of different utterance encoding strategies. We investigate the following strategies:
\begin{enumerate}
  \item Averaging of word2vec/BERT word embedding
  \item Encoding utterances with CNN (with/without word2vec/BERT initalization, with/without `freezing' the embeddings)
  \item BERT encoded sentences (with/without additional unsupervised pretraining on full Switchboard corpus)
  \end{enumerate}

>>>>

Dialogue acts depend on their conversational context.
For example, a speaker may use \textit{okay} to agree with their interlocutor, answer a yes-no question in the affirmative, 
or simply acknowledge the previous utterance, depending on what has transpired in the conversation so far.
Naturally, many DAR /strategies attempt to model discourse context in addition to considering the content of the utterance in question.
\cite{stolckeDialogueActModeling2000}, for example, use a Hidden Markov Model to tag dialogue acts.
The hidden state of neural sequence models can also be used to represent discourse context 
\citep[e.g.][]{kalchbrennerRecurrentConvolutionalNeural2013,tranPreservingDistributionalInformation2017}.

@@

However, given that BERT is pre-trained on book and encyclopedia data, 
there is no guarantee it will improve performance on dialogue-specific tasks.
Adding to that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
To assess BERT's potential for dialogue applications, we propose a series of DAR experiments 
with various utterance encoders, including BERT.
Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts (figure~\ref{fig:architecture}).
In particular, we are interested in whether BERT can be fine-tuned to adequately represent
dialogue-specific features such as discourse markers, disfluencies, and non-verbal vocalizations such as laughter.

@@

%\paragraph{Model.}
%The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
%For the sequence model, we use a simple RNN.
%Conceptually the hidden state of this RNN represents the discourse context which, 
%together with the encoded utterance, is used to predict the discourse act tag.

@@

\paragraph{Experiments.}
Our aim is to test the effectiveness of different utterance encoding strategies. We investigate the following strategies:
\begin{enumerate}
  \item Averaging of word2vec/BERT word embedding
  \item Encoding utterances with CNN (with/without word2vec/BERT initalization, with/without `freezing' the embeddings)
  \item BERT encoded sentences (with/without additional unsupervised pretraining on the full Switchboard corpus)
  \end{enumerate}
